Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-06 paper/paper.tex
New transition for section 2

\section{Known neurobiological properties of the default mode network}
We begin by a deconstruction the overall DMN function
by the mechanistic relevance of each individual network node
based on published findings from neuroscience experiments.
%
\subsection{The posteromedial cortex: Global monitoring and information integration}
Among all parts of the human brain,
the midline structures of the DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are responsible for the highest metabolic turn-over
of glucose energy consumption \citep{raichle2001pnas}.
These metabolic characteristics go hand-in-hand with
brain-imaging analyses \citep{andrews2010} in
suggesting that the PMC and dmPFC
potentially represent the functional backbone of the DMN.

>>>>

\section{Known neurobiological properties of the default mode network}
We begin by a deconstruction of the DMN based on experimental findings in neuroscience. This walkthrough across each individual network node will describe their mechanistic relevance, paving the way for their functional interpretation within our computational account in the next section.

%
\subsection{The posteromedial cortex: Global monitoring and information integration}
Among all parts of the human brain,
the midline structures of the DMN,
including the posteromedial cortex (PMC) and
the medial prefrontal cortex (mPFC),
are responsible for the highest metabolic turn-over
of glucose energy consumption \citep{raichle2001pnas}.
These metabolic characteristics go hand-in-hand with
brain-imaging analyses \citep{andrews2010} in
suggesting that the PMC and dmPFC
potentially represent the functional backbone of the DMN.
